Simulataneous Robot Localization and \\Environment Mapping with \\Simulated Sensor Measurements

### 2018-05-03 paper.tex
Rewording

The simulation for the EKF SLAM algorithm is demonstrated through an abstract robot which 
can sense the two-dimensional environment through multiple types of sensors. To 
simulate the NASA RMC robot, the robot can sense the state of itself and the environment 
obstacles through multiple abstracted types of sensors, including:

@@

The EKF SLAM algorithm was unsuccessful in accurately localizing the robot and landmarks. The 
algorithm was executed using sensor models for the Microsoft Kinect and gyro. Figures \ref{fig:1}-\ref{fig:3}
present the error between the actual and estimated pose of the robot. The estimated $x$ and $y$ positions of the 
robot did not converge to the actual positions, with errors ranging from $-1.5$ meters to $1$ meter. However, 
the estimated angular orientation of the robot closely matched the actual angular orientation with the 
difference staying within $0.2$ radians. This is likely due to the high accuracy of the gyroscope sensor. 
Figures \ref{fig:4}-\ref{fig:6} present the variances for the estimate pose of the robot. The figures clearly demonstrate 
the effects of the prediction and correction step on the variance. The variance for each pose value 
increases during the motion model update and then decreases in the correction step with the sensor 
model updates. This accounts for the sporadic appearance of the data. However, the average variance 
reduces over time and converges to a limit. Figure \ref{fig:7} shows the number of unique landmarks stored in the 
map built by the algorithm. Despite only three landmarks being present in the environment, the algorithm 
identified 254 landmarks, indicating significant errors in data association between new observations and 
previous observations.

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/1-actual-predicted-error-x.jpg}
\caption{}
\label{fig:1}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/2-actual-predicted-error-y.jpg}
\caption{}
\label{fig:2}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/3-actual-predicted-error-theta.jpg}
\caption{}
\label{fig:3}
\end{figure}

>>>>

The simulation for the EKF SLAM algorithm is demonstrated through an abstract robot which 
can sense the two-dimensional environment through multiple types of sensors. The environment consisted of a fiducial marker placed at the origin and three obstacles randomly placed in the obstacle zone. To 
simulate the NASA RMC robot, the robot can sense the state of itself and the environment 
obstacles through multiple abstracted types of sensors, including:

@@

The EKF SLAM algorithm was unsuccessful in accurately localizing the robot and landmarks. The 
algorithm was executed using sensor models for the Microsoft Kinect and gyro. Figures \ref{fig:1}-\ref{fig:3}
present the error between the actual and estimated pose of the robot. The estimated $x$ and $y$ positions of the 
robot did not converge to the actual positions, with errors ranging from $-1.5$ meters to $1$ meter. However, 
the estimated angular orientation of the robot closely matched the actual angular orientation with the 
difference staying within $0.2$ radians. This is likely due to the low standard deviation of the gyroscope sensor. 
Figures \ref{fig:4}-\ref{fig:6} present the variances for the estimate pose of the robot. The figures clearly demonstrate 
the effects of the prediction and correction step on the variance. The variance for each pose value 
increases during the motion model update and then decreases in the correction step with the sensor 
model updates. This accounts for the sporadic appearance of the data. However, the average variance 
reduces over time and converges to a limit. Figure \ref{fig:7} shows the number of unique landmarks stored in the 
map built by the algorithm. Despite only three landmarks being present in the environment, the algorithm 
identified 254 landmarks, indicating significant errors in data association between new observations and 
previous observations.

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/1-actual-predicted-error-x.jpg}
\caption{The difference between the actual and predicted values in the $x$-axis.}
\label{fig:1}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/2-actual-predicted-error-y.jpg}
\caption{The difference between the actual and predicted values in the $y$-axis.}
\label{fig:2}
\end{figure}

\begin{figure}[!t]%{0.35\textwidth}
\centering
\includegraphics[width=0.9\linewidth]{Figures/3-actual-predicted-error-theta.jpg}
\caption{The difference between the actual and predicted values in $\theta$.}
\label{fig:3}
\end{figure}
